### 2016-10-21 capability-machine.tex
restructured proof section to reflect new presentation

\subsection{Worlds}
Assume preordered \cofe{}\ $\Wor$ and isomorphism $\xi$ such that:
\[
  \xi : \Wor \cong \blater (\nats \finparfun (\States \times \Rel \times (\States \fun (\Wor \monnefun \UPred{\HeapSegments}))))
\]
$\xi$ is a morphism in the category $\CatP$ (the category of preordered \cofes{}), so it is non-expansive and monotone.

We now define regions as
\[
\Regions \defeq (\States \times \Rel \times (\States \fun (\Wor \monnefun \UPred{\HeapSegments})))
\]
define region names to be natural numbers, i.e.,
\[
  \RegionNames \defeq \nats
\]
and define worlds as
\[
\Worlds \defeq \RegionNames \finparfun \Regions
\]
To define future worlds and regions, We use the ordering inherited from the preordered \cofes{}.
\begin{definition}[Future worlds]
  For $W, W' \in \Worlds$
 \begin{align*}
 W' \future W & & \text{ iff } & &
   \begin{gathered}
     \dom(W') \supseteq \dom(W)\\ 
     \text{ and } \\
     \forall r \in \dom(W) \ldotp W'(r) \future W(r)
   \end{gathered}
 \end{align*}
\end{definition}

\begin{definition}[Future regions]
For regions $(s_2,\phi_2,H_2), (s_1,\phi_1,H_1) \in \Regions$
  \begin{align*}
 (s_2,\phi_2,H_2) \future (s_1,\phi_1,H_1) &&\text{ iff } & &
(\phi_1,H_1) = (\phi_2,H_2) \text{ and } (s_1,s_2) \in \phi_2
  \end{align*}
\end{definition}

@@

\subsubsection{Continuation Relation}
\label{subsubsection:continuation-relation}
The continuation relation is used in the definition of the expression relation. The continuation relation ensures that if you continue execution through a continuation, then it will result in a good result according to the world.
\begin{align*}
  \stdkr \quad : & \quad (\Worlds \monnefun \UPred{\Words}) \nefun \Worlds \monnefun \UPred{\Words} \\
  \stdkr \defeq & \lambda \stdvr \ldotp \lambda W \ldotp\{ \npair{c} \mid
                     \begin{aligned}[t]
                       & \npair{c} \in \stdvr(W) \land \\
                       &  \forall W' \future W, n' < n\ldotp %on the whiteboard, we had public future world.
                       \forall \heapSat[\hs]{n'}{W'} \ldotp \forall \reg, \npair[n']{reg} \in \stdrr(\stdvr)(W') \ldotp \\
                       & \quad \npair[n']{(reg\update{\pcreg}{\updatePcPerm{\var{c}}},\hs)} \in \observations(W') \}
                 \end{aligned}
\end{align*}
We require the continuation to be in the value relation, because it will have to be in the registers when it is invoked, so to argue that the register file is in the register-file relation, we need to know that the continuation is in the value relation.

@@

\subsubsection{Expression Relation}
\label{subsubsection:expression-relation}
The expression relation is defined as follows:
\begin{align*}
  \stder \quad : & \quad  (\Worlds \monnefun \UPred{\Words}) \nefun \Worlds \nefun \UPred{\Words} \\%TODO: Check whether this needs to be monotone
  \stder \defeq & \lambda \stdvr \ldotp \lambda W \ldotp \{ \npair{\pc} \mid 
  \begin{aligned}[t]
    & \forall n' \leq n \ldotp\\
    & \quad \forall \npair[n']{\reg} \in \stdrr(\stdvr)(W) \ldotp \\
    & \quad \quad \forall \npair[n']{c} \in \stdkr(\stdvr)(W) \ldotp \\
    & \quad \qquad  \forall \heapSat[\hs]{n'}{W} \ldotp \\
    & \quad \qquad \quad \npair[n']{(\reg\update{r_0}{c}\update{\pcreg}{\pc},\hs)} \in \observations(W) \}
  \end{aligned}
\end{align*}
Well-definedness lemmas:
\begin{lemma}[Expression relation uniformity]
\label{lem:stder-dc}
  \begin{align*}
    & \forall \stdvr \ldotp \forall n' \leq n \ldotp \forall W \ldotp \forall \pc \ldotp\\
    & \quad \npair{\pc} \in \stder(\stdvr)(W) \Rightarrow \npair[n']{\pc} \in \stder(\stdvr)(W) 
 \end{align*}
\end{lemma}

@@

@@

\subsection{Well-foundedness lemmas}
\begin{lemma}[Future worlds transitive]
  \begin{align*}
    & \forall W, W', W'' \ldotp \\
    & \quad  W'' \future W' \land W' \future W \Rightarrow W'' \future W
  \end{align*}
\end{lemma}
\begin{proof}
  %TODO
\end{proof}

\begin{lemma}
\label{lem:nequal-and-future-world}
  \begin{align*}
    & \forall W_1,W_2,W_1' \ldotp \\
    & \quad W_1 \nequal W_2 \land W_1' \future W_1 \Rightarrow \\
    & \qquad \exists W_2' \ldotp W_2' \future W_2 \land W_1' \nequal W_2'
  \end{align*}
\end{lemma}
\begin{proof}
  Assume $W_1 \nequal W_2$ and $W_1' \future W_2'$. Define $W_2'$ to have $\dom(W_2')=\dom(W_1')$ where
\[
  W_2' \; r = \left\{
  \begin{aligned}
    & (s_1',\phi_2,H_2) & &\text{for } j \in \dom(W_2) \text{ and } W_2 \; j = (s_2,\phi_2,H_2) \\
    &                  & &\quad \text{ and } W_1' \; j = (s_1',\phi',H_1') \\
    & W_1' \; r        & &\text{otherwise}
  \end{aligned} 
  \right.
\]

\begin{proof}[Proof of lemma~\ref{lem:rc-mono-world}]
Let $\stdvr$, $n$,$W$, $W'$, $b$, and $e$ be given where $W' \future W$. Let $n \in \readCond{}(\stdvr)(\start,\addrend,W)$, this gives an $r$ and $[b',e'] \supseteq [b,e]$ such that $W(r) \nsubeq \iota_{b',e'} (r) = ((b',e'),=,H_{\var{std}})$. This gives
\begin{align*}
  &W(r).\phi \equiv = \\
  &W(r).s    = (b',e') \\
  &\forall \hat{W} \ldotp W(r).H\; (b',e') \; \hat{W} \nsubeq[n-1] H_{\var{std}}\; (b',e') \; \hat{W}
\end{align*}
$W' \future W$ gives
\begin{align*}
  &W'(r).\phi = W(r).\phi \\
  &(W'(r).s,W(r).s) \in W(r).\phi \\
  &W'(r).H = W(r).H \\
 \end{align*}
Combining these two sets of properties line for line, we get the following for $W'$:
\begin{align*}
  & W'(r).\phi \equiv = \\
  & W'(r) = (b',e') \\
  &\forall \hat{W} \ldotp W'(r).H\; (b',e') \; \hat{W} \nsubeq[n-1] H_{\var{std}}\; (b',e') \; \hat{W}
\end{align*}
These are exactly the properties needed to get $W'(r) \nsubeq \iota_{b',e'} (r)$ which is exactly the result we want.
\end{proof}

\begin{proof}[Proof of lemma~\ref{lem:rc-ne-world}]
Assume 
\[
  (b,e,W) \nequal (b,e,W')
\]
which implies $W \nequal W'$. Now let $(n,\hs) \in \readCond{}(\stdvr)(b,e,W)$ be given. This gives us $r$ and $[b',e'] \supseteq [b,e]$ such that 
\[
  W(r) \nsubeq[n-1] \iota_{b',e'}(\stdvr)
\]
Using $r$ and $[b',e']$, we need to show
\[
  W'(r) \nsubeq[n-1] \iota_{b',e'}(\stdvr)
\]
Let $W(r) = (s,\phi,H)$, $W(r) = (s',\phi',H')$, and $\iota_{b',e'} = (s_\iota,\phi_\iota,H_\iota)$.
From the $n$-equality of our worlds, we get $W(r) \nequal W'(r)$. From this we conclude
\[
  (s',\phi') = (s,\phi) = (s_\iota,\phi_\iota)
\]
It remains to show
\[
  \forall \hat{W} \in \Wor \ldotp H' \; s \; W \nequal[n-1] H_\iota \; s \; W
\]
Given $\hat{W}$ we know from $n$-equality of the worlds
\[
   H' \; s \; \hat{W} \nequal H \; s \; \hat{W}
\]
Given $(k,\hs) \in H' \; s \; W$ where $k < n$ and $\hs$ is a heap segment, by above we have $(k,\hs) \in H \; s \; W$ and from the $\nsubeq[n-1]$ assumption, we get $(k,\hs) \in H_\iota \; s_\iota \; W$.
\end{proof}

\begin{proof}[Proof of lemma~\ref{lem:wc-dc}]
  Follows directly from the definition.
\end{proof}

\begin{proof}[Proof of lemma~\ref{lem:wc-mono-world}]
  Similar to the proof of the monotonicity of the read condition.
\end{proof}

\begin{proof}[Proof of lemma~\ref{lem:ec-dc}]
  Follows directly from definition: Let $\stdvr$, $n$, $n'$, $W$, $\start$, and $\addrend$ be given. Assume $n \in \execCond{}(\stdvr)(\start,\addrend,\perm,W)$ and $n' \leq n$. If $n' = n$, then the result follows directly from assumption. If $n' < n$, then let $n'' < n'$, $W' \future W$, and $a \in [\start,\addrend]$ be given. Using that we by transitivity have $n'' < n$, we get the desired result from assumption.
\end{proof}

\begin{proof}[Proof of lemma~\ref{lem:ec-mono-world}]
  Follows directly from definition.
\end{proof}

\begin{proof}[Proof of lemma~\ref{lem:ec-ne-world}]
  Assume $(\start,\addrend,\perm,W_1) \nequal (\start,\addrend,\perm,W_2)$ and thus $W_1 \nequal W_2$. Given $n'<n$, $W_1' \future W_1$, and $\addr$, show
\[
  \npair[n']{(\perm,\start,\addrend,\addr)} \in \stder(\stdvr)(W_1')
\]
by lemma~\ref{lem:nequal-and-future-world} there must exist $W_2'$ such that $W_2' \future W_2$ and $W_2' \nequal W_1'$. By assumption $n \in \execCond{}(\stdvr)(\start,\addrend,\perm,W_2)$ we have
\[
\npair[n']{(\perm,\start,\addrend,\addr)} \in \stder(\stdvr)(W_2')
\]
and by non-expansiveness of $\stder(\stdvr)$ (lemma~\ref{lem:stder-ne-worlds}), we get the desired result.
\end{proof}

\begin{lemma}[Write condition implies read condition]
\label{lem:wc-implies-rc}
  \begin{align*}
    &\forall n, W, \start, \addrend \ldotp\\ 
    &\quad \writeCond{n,W,\start,\addrend} \Rightarrow \readCond{n,W,\start,\addrend}
  \end{align*}
\end{lemma}[Proof of lemma~\ref{lem:wc-implies-rc}]
\begin{proof}
  Follows directly from the definition.
\end{proof}

\begin{lemma}[Value relation uniformity]
\label{lem:stdvr-uniform-step}
  \begin{align*}
    &\forall n' < n \ldotp \forall W \ldotp \forall w \ldotp\\
    &\quad \npair{w} \in \stdvr(W) \Rightarrow \npair[n']{w} \in \stdvr(W)
  \end{align*}
\end{lemma}
\begin{proof}
  Follows from the uniformity of $\readCond{}$, $\writeCond{}$, $\execCond{}$, and $\entryCond{}$.
\end{proof}

\begin{lemma}[Value relation monotone in worlds]
  \begin{align*}
    &\forall n \ldotp \forall W' \future W \ldotp \forall w \ldotp\\ 
    &\quad \npair{w} \in \stdvr(W) \Rightarrow \npair{w} \in \stdvr(W')
  \end{align*}
\end{lemma}
\begin{proof}
  Follows from uniformity of $\readCond{}$, $\writeCond{}$, $\execCond{}$, and $\entryCond{}$ in the worlds. That is Lemma~\ref{lem:rc-mono-world},~\ref{lem:wc-mono-world},~\ref{lem:ec-mono-world}, and~\ref{lem:en-mono-world}.
\end{proof}

\begin{lemma}[Value relation contractive]
  \begin{align*}
    & \forall n \ldotp \forall W \in \Worlds \forall w \ldotp \\
    & \quad \npair[n]{w} \in \stdvr(W) \Rightarrow \\
    & \qquad \npair[n+1]{w} \in \stdvr(W)
  \end{align*}
\end{lemma}
\begin{proof}
  %TODO
\end{proof}

\begin{proof}[Proof of lemma~\ref{lem:obs-dc}]
  Let $n' < n$, $W$, $\reg$, and $\hs$ be given. Assume $\npair{(\reg,\hs)} \in \observations(W)$. Let $\heap_f$, $heap'$, $i \leq n'$ be given and assume $(\reg, \hs \uplus \heap_f) \step[i] (\halted, \heap')$. By assumption, we have a $W' \future W$ and $\hs'$ such that
  \begin{align}
&\heap' = \hs' \uplus \heap_f \label{lem:eq:stdvr1}\\
&\heapSat[\hs']{n-i}{W'}\label{lem:eq:stdvr2}
  \end{align}. 
Using $W'$ and $\hs'$ as existential witnesses, we already have Equation~\ref{lem:eq:stdvr1} as the first necessary condition and from the above heap satisfaction along with heap satisfaction being uniform in $n$, we get $\heapSat[\hs']{n'-i}{W'}$. These are the two conditions necessary to get $\npair[n']{(\reg,\hs)} \in \observations(W)$.
\end{proof}

\begin{proof}[Proof of lemma~\ref{lem:reg-dc}]
  %TODO
\end{proof}

\begin{proof}[Proof of lemma~\ref{lem:reg-mono-worlds}]
  This follows by monotonicity of $\stdvr$ in the worlds.
\end{proof}

\begin{proof}[Proof of lemma~\ref{lem:stdkr-dc}]
Follows by using the assumption and transitivity of inequality.
\end{proof}

\begin{proof}[Proof of lemma~\ref{lem:stdkr-mono-worlds}]
We need to show two things: The continuation is in the value predicate in the future world and that continuing execution using the continuation is in the observation predicate.

The first follows from the value predicate being monotone in the world.

The second property follows by assumption and transitivity of future worlds.
\end{proof}

\begin{proof}[Proof of lemma~\ref{lem:stder-dc}]
  Follows from the assumption.
\end{proof}

\begin{proof}[Proof of lemma~\ref{lem:stder-ne-vr}]
    %TODO
\end{proof}
\section{Other examples and applications}
\label{sec:other_apps}
This section contains some ideas about other examples and applications than the
ticket dispenser example.

@@

\begin{appendices}
\section{Definitions and Proofs related to Section~\ref{subsec:recursive-dom-eq}}
\end{appendices}

@@

\section{Proof of Lemmas in Section~\ref{subsec:further-standard-regions}}
\begin{proof}[Proof of Lemma~\ref{lem:std-reg-mono-world}]
  %TODO
\end{proof}

@@

\begin{proof}[Proof of Lemma~\ref{lem:std-z-region-wd}]
  %TODO
\end{proof}

>>>>

\subsection{Worlds}
\label{subsec:worlds}
Assume preordered \cofe{}\ $\Wor$ and isomorphism $\xi$ such that:
\[
  \xi : \Wor \cong \blater (\nats \finparfun (\States \times \Rel \times (\States \fun (\Wor \monnefun \UPred{\HeapSegments}))))
\]
$\xi$ is a morphism in the category $\CatP$ (the category of preordered \cofes{}), so it is non-expansive and monotone.

We now define regions as
\[
\Regions \defeq (\States \times \Rel \times (\States \fun (\Wor \monnefun \UPred{\HeapSegments})))
\]
define region names to be natural numbers, i.e.,
\[
  \RegionNames \defeq \nats
\]
and define worlds as
\[
\Worlds \defeq \RegionNames \finparfun \Regions
\]
To define future worlds and regions, We use the ordering inherited from the preordered \cofes{}.
\begin{definition}[Future regions]
For regions $(s_2,\phi_2,H_2), (s_1,\phi_1,H_1) \in \Regions$
  \begin{align*}
 (s_2,\phi_2,H_2) \future (s_1,\phi_1,H_1) &&\text{ iff } & &
(\phi_1,H_1) = (\phi_2,H_2) \text{ and } (s_1,s_2) \in \phi_2
  \end{align*}
\end{definition}

\begin{definition}[Future worlds]
  For $W, W' \in \Worlds$
 \begin{align*}
 W' \future W & & \text{ iff } & &
   \begin{gathered}
     \dom(W') \supseteq \dom(W)\\ 
     \text{ and } \\
     \forall r \in \dom(W) \ldotp W'(r) \future W(r)
   \end{gathered}
 \end{align*}
\end{definition}

\begin{lemma}[Future worlds transitive]
\label{lem:future-worlds-trans}
  \begin{align*}
    & \forall W, W', W'' \ldotp \\
    & \quad  W'' \future W' \land W' \future W \Rightarrow W'' \future W
  \end{align*}
\end{lemma}

\begin{lemma}
\label{lem:nequal-and-future-world}
  \begin{align*}
    & \forall W_1,W_2,W_1' \ldotp \\
    & \quad W_1 \nequal W_2 \land W_1' \future W_1 \Rightarrow \\
    & \qquad \exists W_2' \ldotp W_2' \future W_2 \land W_1' \nequal W_2'
  \end{align*}
\end{lemma}

@@

\subsubsection{Continuation Relation}
\label{subsubsec:continuation-relation}
The continuation relation is used in the definition of the expression relation. The continuation relation ensures that if you continue execution through a continuation, then it will result in a good result according to the world.
\begin{align*}
  \stdkr \quad : & \quad (\Worlds \monnefun \UPred{\Words}) \nefun \Worlds \monnefun \UPred{\Words} \\
  \stdkr \defeq & \lambda \stdvr \ldotp \lambda W \ldotp\{ \npair{c} \mid
                     \begin{aligned}[t]
                       & \npair{c} \in \stdvr(W) \land \\
                       &  \forall W' \future W, n' < n\ldotp %on the whiteboard, we had public future world.
                       \forall \heapSat[\hs]{n'}{W'} \ldotp \forall \reg, \npair[n']{reg} \in \stdrr(\stdvr)(W') \ldotp \\
                       & \quad \npair[n']{(reg\update{\pcreg}{\updatePcPerm{\var{c}}},\hs)} \in \observations(W') \}
                 \end{aligned}
\end{align*}
We require the continuation to be in the value relation, because it will have to be in the registers when it is invoked, so to argue that the register file is in the register-file relation, we need to know that the continuation is in the value relation.

@@

\subsubsection{Expression Relation}
\label{subsubsec:expression-relation}
The expression relation is defined as follows:
\begin{align*}
  \stder \quad : & \quad  (\Worlds \monnefun \UPred{\Words}) \nefun \Worlds \nefun \UPred{\Words} \\%TODO: Check whether this needs to be monotone
  \stder \defeq & \lambda \stdvr \ldotp \lambda W \ldotp \{ \npair{\pc} \mid 
  \begin{aligned}[t]
    & \forall n' \leq n \ldotp\\
    & \quad \forall \npair[n']{\reg} \in \stdrr(\stdvr)(W) \ldotp \\
    & \quad \quad \forall \npair[n']{c} \in \stdkr(\stdvr)(W) \ldotp \\
    & \quad \qquad  \forall \heapSat[\hs]{n'}{W} \ldotp \\
    & \quad \qquad \quad \npair[n']{(\reg\update{r_0}{c}\update{\pcreg}{\pc},\hs)} \in \observations(W) \}
  \end{aligned}
\end{align*}
Well-definedness lemmas:
\begin{lemma}[Expression relation uniformity]
\label{lem:stder-dc}
  \begin{align*}
    & \forall \stdvr \ldotp \forall n' \leq n \ldotp \forall W \ldotp \forall \pc \ldotp\\
    & \quad \npair{\pc} \in \stder(\stdvr)(W) \Rightarrow \npair[n']{\pc} \in \stder(\stdvr)(W) 
 \end{align*}
\end{lemma}

@@

\begin{lemma}[Write condition implies read condition]
\label{lem:wc-implies-rc}
  \begin{align*}
    &\forall n, W, \start, \addrend \ldotp\\ 
    &\quad \writeCond{n,W,\start,\addrend} \Rightarrow \readCond{n,W,\start,\addrend}
  \end{align*}
\end{lemma}

@@

\section{Other examples and applications}
\label{sec:other_apps}
This section contains some ideas about other examples and applications than the
ticket dispenser example.

@@

\begin{appendices}

\section{Proofs of Lemmas in Section~\ref{sec:logical-relation}}
\subsection{Definitions and Proofs related to Section~\ref{subsec:recursive-dom-eq}}

@@

\end{proof}
\subsection{Proofs of Lemmas in Section~\ref{subsec:worlds}}
%TODO All proofs written by hand, typeset them.
\begin{proof}[Proof of lemma~\ref{lem:nequal-and-future-world}]
  Assume $W_1 \nequal W_2$ and $W_1' \future W_2'$. Define $W_2'$ to have $\dom(W_2')=\dom(W_1')$ where
\[
  W_2' \; r = \left\{
  \begin{aligned}
    & (s_1',\phi_2,H_2) & &\text{for } j \in \dom(W_2) \text{ and } W_2 \; j = (s_2,\phi_2,H_2) \\
    &                  & &\quad \text{ and } W_1' \; j = (s_1',\phi',H_1') \\
    & W_1' \; r        & &\text{otherwise}
  \end{aligned} 
  \right.
\]

\subsection{Proofs of Lemmas in Section~\ref{subsec:logical-relation-setup}}
%All the lemmas are in subsections.
\subsubsection{Proofs of Lemmas in Section~\ref{subsubsec:observation-relation}}
%TODO All proofs written by hand (but one), typeset them.
\begin{proof}[Proof of lemma~\ref{lem:obs-dc}]
  Let $n' < n$, $W$, $\reg$, and $\hs$ be given. Assume $\npair{(\reg,\hs)} \in \observations(W)$. Let $\heap_f$, $heap'$, $i \leq n'$ be given and assume $(\reg, \hs \uplus \heap_f) \step[i] (\halted, \heap')$. By assumption, we have a $W' \future W$ and $\hs'$ such that
  \begin{align}
&\heap' = \hs' \uplus \heap_f \label{lem:eq:stdvr1}\\
&\heapSat[\hs']{n-i}{W'}\label{lem:eq:stdvr2}
  \end{align}. 
Using $W'$ and $\hs'$ as existential witnesses, we already have Equation~\ref{lem:eq:stdvr1} as the first necessary condition and from the above heap satisfaction along with heap satisfaction being uniform in $n$, we get $\heapSat[\hs']{n'-i}{W'}$. These are the two conditions necessary to get $\npair[n']{(\reg,\hs)} \in \observations(W)$.
\end{proof}

\subsubsection{Proofs of Lemmas in Section~\ref{subsubsec:register-file-relation}}
%TODO All proof but one proof written by hand, typeset them.
%TODO missing proof register relation ne in worlds.
\begin{proof}[Proof of lemma~\ref{lem:reg-dc}]
  %TODO
\end{proof}

\begin{proof}[Proof of lemma~\ref{lem:reg-mono-worlds}]
 %TODO,  This follows by monotonicity of $\stdvr$ in the worlds.
\end{proof}

\subsubsection{Proofs of Lemmas in Section~\ref{subsubsec:continuation-relation}}
%TODO All proof but one proof written by hand, typeset them.
%TODO missing proof continuation relation ne in worlds.
\begin{proof}[Proof of lemma~\ref{lem:stdkr-dc}]
  % TODO, Follows by using the assumption and transitivity of inequality.
\end{proof}

\begin{proof}[Proof of lemma~\ref{lem:stdkr-mono-worlds}]
  % TODO
\end{proof}

\subsubsection{Proofs of Lemmas in Section~\ref{subsubsec:expression-relation}}
%TODO All proofs written by hand, typeset them.
\begin{proof}[Proof of lemma~\ref{lem:stder-dc}]
  %TODO,  Follows from the assumption.
\end{proof}

\begin{proof}[Proof of lemma~\ref{lem:stder-ne-vr}]
  %TODO
\end{proof}

\subsubsection{Proofs of Lemmas in Section~\ref{subsubsec:standard-region}}
%TODO All proofs written by hand, typeset them.
\begin{proof}[Proof of Lemma~\ref{lem:std-reg-mono-world}]
  %TODO
\end{proof}

@@

\subsubsection{Proofs of Lemmas in Section~\ref{subsubsec:capability-conditions}}
%TODO All proofs written by hand, typeset them.

\begin{proof}[Proof of lemma~\ref{lem:rc-mono-world}]
%TODO
\end{proof}
\begin{proof}[Proof of lemma~\ref{lem:rc-ne-world}]
%TODO
\end{proof}
\begin{proof}[Proof of lemma~\ref{lem:wc-dc}]
%TODO, Follows directly from the definition.
\end{proof}

\begin{proof}[Proof of lemma~\ref{lem:wc-mono-world}]
%TODO, Similar to the proof of the monotonicity of the read condition.
\end{proof}

\begin{proof}[Proof of lemma~\ref{lem:ec-dc}]
%TODO
\end{proof}

\begin{proof}[Proof of lemma~\ref{lem:ec-mono-world}]
%TODO, Follows directly from definition.
\end{proof}

\begin{proof}[Proof of lemma~\ref{lem:ec-ne-world}]
%TODO 
\end{proof}

\begin{proof}[Proof of lemma~\ref{lem:wc-implies-rc}]
  Follows directly from the definition.
\end{proof}

\subsubsection{Proofs of Lemmas in Section~\ref{subsubsec:value-relation}}
%TODO All proofs written by hand, typeset them.
\begin{proof}[Proof of lemma~\ref{lem:stdvr-dc}]
  Follows from the uniformity of $\readCond{}$, $\writeCond{}$, $\execCond{}$, and $\entryCond{}$.
  %TODO show one case to illustrate the above, refer to the lemmas in question
\end{proof}

\begin{proof}[Proof of lemma~\ref{lem:stdvr-ne-V}]
  %TODO
\end{proof}

\begin{proof}[Proof of lemma~\ref{lem:stdvr-mono-world}]
  Follows from monotonicity of $\readCond{}$, $\writeCond{}$, $\execCond{}$, and $\entryCond{}$ in the worlds. That is Lemma~\ref{lem:rc-mono-world},~\ref{lem:wc-mono-world},~\ref{lem:ec-mono-world}, and~\ref{lem:en-mono-world}.
  %TODO show one case to illustrate the above
\end{proof}

\begin{proof}[Proof of lemma~\ref{lem:stdvr-ne-worlds}]
  %TODO
\end{proof}

\begin{proof}[Proof of lemma~\ref{lem:stdvr-con}]
  %TODO
\end{proof}

\subsection{Proofs of Lemmas in Section~\ref{subsec:further-standard-regions}}
%TODO all the proofs need to be done.

\begin{proof}[Proof of Lemma~\ref{lem:std-z-region-wd}]
  %TODO
\end{proof}
\end{appendices}
